**Cover sheet:**

This report was created using data last queried at **`r query_run_time`.**

The main parameters used in this survey report are:



**Current survey year:**
```{r cover_sheet_current_survey, echo = FALSE, message=FALSE, warning=FALSE, results='asis'}

# build table for the current survey
regions <- current_year_pollock_biomass_nums %>%
  distinct(SURVEY, region) %>%
  group_by(SURVEY) %>%
  summarize(regions = paste(region, collapse = ", "))

current_year_summary_table <- left_join(current_year_query_params, regions, by = c('surveys' = 'SURVEY')) %>%
  arrange(surveys)

current_year_summary_table <- flextable(current_year_summary_table) %>%
  flextable::colformat_num(j = c("surveys"), big.mark = "") %>%
  flextable::width(j = 1:5, width = .7, unit = 'in') %>%
  flextable::width(j = 6, width = 2.3, unit = 'in') %>%
  flextable::fontsize(size= 8, part = 'all')


#print table
flextable_to_rmd(x = current_year_summary_table, ft.align = "left", ft.split = FALSE, ft.keepnext = FALSE, print = TRUE)

```

**The past:**

```{r cover_sheet_historical, echo = FALSE, message=FALSE, warning=FALSE, results='asis',  fig.width=6.5}

# build table for the historical survey- organize by region
regions <- all_species_biomass_nums %>%
  distinct(SURVEY, region) %>%
  group_by(SURVEY) %>%
  summarize(regions = paste(region, collapse = ", "))

historical_cover_sheet <- left_join(historical_params, regions, by = c('surveys' = 'SURVEY')) %>%
  arrange(surveys) %>%
  select(- report_nums)

#historical_cover_sheet <- historical_params

historical_cover_sheet <- flextable(historical_cover_sheet)  %>%
  flextable::colformat_num(j = c("surveys"), big.mark = "")  %>%
  flextable::width(j = 1:5, width = .7, unit = 'in') %>%
  flextable::width(j = 6, width = 2.3, unit = 'in') %>%
  flextable::fontsize(size= 8, part = 'all')

# print table
flextable_to_rmd(x = historical_cover_sheet, ft.align = "left", ft.split = TRUE, ft.keepnext = FALSE, print = TRUE)

```

The table(s) above highlights the parameters used to grab historical data. Check out the other parameters in the top of the script 'main_cruise_report_YYYY.Rmd' to be safe!  **Bold text will likely require updates as you edit the draft!**

\pagebreak