
```{r echo = FALSE, message=FALSE, warning=FALSE}
# identify the requested report region
region_id <- "Bogoslof"

# subset the region of interest from intervals
region_interval_data <- current_year_interval_data

# subset the events in the region of interest- events
region_event_data <- current_year_event_data

# subset the specimen table data-
region_specimen_data <- specimen_table_data

# and the catch table....
# subset the specimen table data-
region_catch_data <- catch_table_data

# use the subset of haul data to make sure you are ONLY getting maturity data
maturities_and_weights <- maturities_and_weights

# identify the survey years
# survey year is grabbed from the 'common values' on the main script
# get the value for the previous survey year- this should work in cases where we skip a year as it just
# sorts all survey years and finds the next in line
survey_years <- -desc(sort(unique(all_species_biomass_nums$year)))
last_year <- survey_years[length(survey_years) - 1]


### Basic survey info: region name, survey dates, total area surveyed, min/max depth, total trackline.
# format start date/end date as Day Month, i.e. '4 June'
start_date <- paste(
  lubridate::day(min(region_interval_data$START_TIME)),
  lubridate::month(min(region_interval_data$START_TIME), label = TRUE, abbr = FALSE)
)


end_date <- paste(
  lubridate::day(max(region_interval_data$START_TIME)),
  lubridate::month(max(region_interval_data$START_TIME), label = TRUE, abbr = FALSE)
)

# get the total area surveyed as sum(interval_length * interval_width); set all intervals as 0.5 nmi length
# as this is what's used in calcs
# report totals in nmi2 and km2
total_survey_area_nmi2 <- sum(0.5 * region_interval_data$INTERVAL_WIDTH, na.rm = TRUE)
total_survey_area_km2 <- sum((0.5 * 1.852) * (region_interval_data$INTERVAL_WIDTH * 1.852), na.rm = TRUE)

# get total transect length/width by report number; use Mode function to report the most common spacing
transect_stats <- region_interval_data %>%
  summarize(
    transect_length_nmi = sum(LENGTH),
    transect_length_km = sum(LENGTH) * 1.852,
    min_bot_depth = min(MEAN_BOTTOM_DEPTH, na.rm = TRUE),
    max_bot_depth = max(MEAN_BOTTOM_DEPTH, na.rm = TRUE),
    min_spacing_nmi = min(INTERVAL_WIDTH, na.rm = TRUE),
    min_spacing_km = min(INTERVAL_WIDTH, na.rm = TRUE) * 1.852,
    max_spacing_nmi = max(INTERVAL_WIDTH, na.rm = TRUE),
    max_spacing_km = max(INTERVAL_WIDTH, na.rm = TRUE) * 1.852,
    primary_spacing_nmi = Mode(INTERVAL_WIDTH),
    primary_spacing_km = Mode(INTERVAL_WIDTH) * 1.852
  )
```

# RESULTS AND DISCUSSION {#results}

## Acoustic System Calibration

Pre-survey calibration measurements of the 38 kHz echosounder showed no notable differences in on-axis gain parameters or beam pattern characteristics confirming that the acoustic system was stable throughout the survey (Table \@ref(tab:caltable)). At 38 kHz the integration gain differed by \< 0.02 dB across the two measurements. On-axis acoustic system gain, $s_{A}$ correction values, and EK80 calibration utility 3 dB beamwidths and offset angles measured during the winter 2024 calibrations were averaged in the linear domain. These averaged values were used with the nominal sound speed and absorption values appropriate for the survey areas in the final parameter set for survey data analysis. The measured equivalent beam angle recorded on the 38 kHz transducer’s specification sheet was adjusted [@Bodholt_2002] using the sound speed assumed during survey conditions for data analysis (Table \@ref(tab:caltable)).


*Survey timing and extent*

The `r current_year` winter AT survey of pre-spawning pollock in `r region_id` was conducted between `r start_date` and `r end_date`.  Poor weather conditions restricted the survey operations from the originally planned timing.  At the beginning of the survey, the weather and sea conditions were unfavorable for beginning the survey transects and collecting biological samples. Due to the delay, transect spacing was reduced in areas with historically low pollock biomass and only two successful trawl samples were conducted. The entire survey area encompassed `r  print_n_decimal(total_survey_area_km2, 0)` km^2^ (`r print_n_decimal(total_survey_area_nmi2, 0)` nmi^2^). Acoustic backscatter was measured along `r print_n_decimal(transect_stats$transect_length_km, 1)` km (`r print_n_decimal(transect_stats$transect_length_nmi, 1) ` nmi) of transects spaced mainly `r round(transect_stats$primary_spacing_km, digits = 1) ` km (`r round(transect_stats$primary_spacing_nmi, digits = 1) ` nmi) apart, with spacing varying from `r round(transect_stats$min_spacing_km, digits = 1) ` km to `r round(transect_stats$max_spacing_km, digits = 1) ` km (`r round(transect_stats$min_spacing_nmi, digits = 1)` to `r round(transect_stats$max_spacing_nmi, digits = 1)` nmi) in the survey area (Fig. \@ref(fig:surveylocationmap)). Bottom depths in the survey area ranged from `r round(transect_stats$min_bot_depth, digits=0) ` m to `r round(transect_stats$max_bot_depth, digits=0) ` m. 

*Environmental conditions*

```{r echo = FALSE, message=FALSE, warning=FALSE}
#### Pull out the SST data for the region of interest.....

# compare sea surface temps at fishing locations to the historical sea surface temps- these values are returned
# from the function 'plot_historical_sst_at_fishing_locs' as:
# list item 2: historical mean

region_sst <- plot_historical_sst_anomalies(historical_sst_scs = historical_scs_sst)

annual_mean_sst <- region_sst[[2]]

# pull the historical mean, and last year's value, from here
last_year_mean_sst_scs <- mean(annual_mean_sst$mean_sst_scs[annual_mean_sst$year == last_year])
survey_year_mean_sst_scs <- mean(annual_mean_sst$mean_sst_scs[annual_mean_sst$year == current_year])

# characterize current survey year conditions relative to historical SCS SST mean
survey_year_conditions <- "average"
if (annual_mean_sst$sst_scs_anomaly[annual_mean_sst$year == current_year] >= abs(0.5)) {
  survey_year_conditions <- ifelse(annual_mean_sst$sst_scs_anomaly[annual_mean_sst$year == current_year] >= 0.5, "warmer", "cooler")
}


### SBE profiles by pollock size class
# get the surface/gear temps for the requested region from the hauls data table
gear_table_for_region <- haul_table_data

stemp <- NULL
stemp_sd <- NULL
gtemp <- NULL
gtemp_sd <- NULL
tdiff <- NULL

# If stats for a single set of all SBE profiles is presented
if (SBE_Nset == 1) {
  stemp <- list(mean(gear_table_for_region$SURFACE_TEMP, na.rm = TRUE))
  gtemp <- list(mean(gear_table_for_region$HEAD_ROPE_TEMP, na.rm = TRUE))
  tdiff <- list(mean(gear_table_for_region$SURFACE_TEMP, na.rm = TRUE) - mean(gear_table_for_region$HEAD_ROPE_TEMP, na.rm = TRUE))
}
# If stats for multiple sets of SBE profiles are presented
if (SBE_Nset >= 2) {
  for (s in 1:SBE_Nset) {
    stemp[s] <- list(mean(gear_table_for_region$SURFACE_TEMP[gear_table_for_region$EVENT_ID %in% SBE_set.ls[[s]]], na.rm = TRUE))
    stemp_sd[s] <- list(sd(gear_table_for_region$SURFACE_TEMP[gear_table_for_region$EVENT_ID %in% SBE_set.ls[[s]]], na.rm = TRUE))
    gtemp[s] <- list(mean(gear_table_for_region$HEAD_ROPE_TEMP[gear_table_for_region$EVENT_ID %in% SBE_set.ls[[s]]], na.rm = TRUE))
    gtemp_sd[s] <- list(sd(gear_table_for_region$HEAD_ROPE_TEMP[gear_table_for_region$EVENT_ID %in% SBE_set.ls[[s]]], na.rm = TRUE))
    tdiff[s] <- list(stemp[[s]] - gtemp[[s]])
  }
}



```

Sea surface temperatures (SST) measured `r current_year` indicate relatively `r survey_year_conditions` thermal conditions during the survey. SST ranged from `r round(scs_summary$min_temp, digits=1)`°C to `r round(scs_summary$max_temp, digits=1)`°C as measured by the ship's flow-through instrumentation along acoustic transects and averaged `r round(scs_summary$mean_temp, digits =1)`°C (Fig. \@ref(fig:shelikofSST)). The along-transect mean SST was `r ifelse(round(abs(survey_year_mean_sst_scs - last_year_mean_sst_scs), digits = 1)>0, paste0(round(abs(survey_year_mean_sst_scs - last_year_mean_sst_scs), digits = 1),'°C ',ifelse(survey_year_mean_sst_scs > last_year_mean_sst_scs, 'warmer than', 'cooler than')), 'the same as')` observed during `r last_year`. The mean SST was very similar to the mean of SST measurements since 2007, indicating a year with average conditions (Fig. \@ref(fig:ssthistoric)). Mean temperature between the surface and deepest trawl (i.e. headrope) depth at all haul locations varied by approximately `r abs(round(mean(gear_table_for_region$SURFACE_TEMP, na.rm = TRUE) - mean(gear_table_for_region$HEAD_ROPE_TEMP, na.rm = TRUE), digits=1))`°C (Fig. \@ref(fig:bogoslofsbe)).

*Trawl Catch Summary*

```{r echo = FALSE, message=FALSE, warning=FALSE}
# get all the gear types, and build a list that separates them by commas or 'and' as needed
gear_names <- unique(as.character(region_event_data$"Gear type"))

gear_counts <- list()

for (i in 1:length(gear_names)) {
  gear_counts[i] <- sum((region_event_data$"Gear type" == gear_names[i]), na.rm = TRUE)-1
}

# get the counts of different haul types for the text
gearboth <- paste0(gear_counts, (paste0(" ", gear_names)))
gearboth <- knitr::combine_words(gearboth)

# query out counts of fork length measurements and ages for the different hauls...
# this information has already been gathered for the 's_specimen_table_data' dataset;
# we'll add the gear information to this dataset
specimen_text_data <- left_join(region_specimen_data,
  st_drop_geometry(region_event_data),
  by = c("SURVEY", "HAUL" = "EVENT_ID", "region")
)



# For other years all fish-containing hauls are used
specimen_region_summary <- specimen_text_data %>%
  rename(gear_type = "Gear type") %>%
  summarize(
    n_lengths = mean(CATCH_LENGTHS, na.rm = TRUE),
    n_weights = mean(WEIGHTS, na.rm = TRUE),
    n_maturities = mean(MATURITIES, na.rm = TRUE),
    n_ages = mean(OTOLITHS, na.rm = TRUE),
    n_all = mean(c(WEIGHTS, MATURITIES, OTOLITHS, OVARY_WEIGHTS), na.rm = TRUE),
    n_hauls = n()
  )


# Catch summary by gear by weight
catchbyarea_LFS <- region_catch_data %>%
  # report LFS hauls only from requested region
  filter(GEAR == "LFS1421") %>%
  group_by(GEAR) %>%
  # make sure table is ordered by weight for reporting in text
  arrange(desc(TOT_WEIGHT)) %>%
  # get 'nice' names to print
  mutate(COMMON_NAME = map_chr(COMMON_NAME, print_species_name))

# Catch summary by gear by number
catchbyarea2_LFS <- region_catch_data %>%
  # report LFS hauls only from requested region
  filter(GEAR == "LFS1421") %>%
  group_by(GEAR) %>%
  # make sure table is ordered by weight for reporting in text
  arrange(desc(TOT_NUMBER)) %>%
  # get 'nice' names to print
  mutate(COMMON_NAME = map_chr(COMMON_NAME, print_species_name))

# If any PNEs were conducted, build a summary of top two items
if (any(region_catch_data$GEAR == "PNE")) {
  catchbyarea_PNE <- region_catch_data %>%
    # report LFS hauls only from requested region
    filter(GEAR == "PNE") %>%
    group_by(GEAR) %>%
    # make sure table is ordered by weight for reporting in text
    arrange(desc(TOT_WEIGHT)) %>%
    # get 'nice' names to print
    mutate(COMMON_NAME = map_chr(COMMON_NAME, print_species_name))

  # build the PNE statement
  pne_statement <- paste(.simpleCap(catchbyarea_PNE$COMMON_NAME[1]), "and", catchbyarea_PNE$COMMON_NAME[2], ifelse((catchbyarea_PNE$COMMON_NAME[1] == catchbyarea_LFS$COMMON_NAME[1] & catchbyarea_PNE$COMMON_NAME[2] == catchbyarea_LFS$COMMON_NAME[2]), "were also", "were"), "the most abundant species in the PNE", ifelse(gear_counts[[2]][1] > 1, "hauls", "haul"), "contributing", round(catchbyarea_PNE$TOT_WEIGHT[1] / sum(catchbyarea_PNE$TOT_WEIGHT) * 100, digits = 1), "% and", round(catchbyarea_PNE$TOT_WEIGHT[2] / sum(catchbyarea_PNE$TOT_WEIGHT) * 100, digits = 1), "% of the total catch by weight and", round(catchbyarea_PNE$TOT_NUMBER[1] / sum(catchbyarea_PNE$TOT_NUMBER) * 100, digits = 1), "% and", round(catchbyarea_PNE$TOT_NUMBER[2] / sum(catchbyarea_PNE$TOT_NUMBER) * 100, digits = 1), "% of the total catch by numbers, respectively (Table \\@ref(tab:shelikofstraitpne)).")
}

# if there were no PNEs, print nothing
if (!any(region_catch_data$GEAR == "PNE")) {
  pne_statement <- c()
}
```

Biological data and specimens were collected in `r region_id` from `r gearboth ` hauls (Table \@ref(tab:surveyhaultable), Fig. \@ref(fig:surveylocationmap)) targeted on backscatter attributed to pollock. The lengths of an average of `r round(specimen_region_summary$n_lengths, digits = 0) `  randomly selected pollock were measured from each haul, with an average of `r round(specimen_region_summary$n_ages, digits = 0) ` individuals more extensively sampled for at least one of the following: body weight, maturity, and age (Table \@ref(tab:surveyspecimen)). A total of `r sum(specimen_text_data$OTOLITHS, na.rm = TRUE) ` otoliths used to estimate pollock ages were collected in the `r region_id` region (Table \@ref(tab:surveyspecimen)). 

 `r .simpleCap(catchbyarea_LFS$COMMON_NAME[1])` and `r catchbyarea_LFS$COMMON_NAME[2]` were the most abundant species by weight in the LFS1421 hauls, contributing `r round(catchbyarea_LFS$TOT_WEIGHT[1]/sum(catchbyarea_LFS$TOT_WEIGHT)*100, digits = 1)`% and `r round(catchbyarea_LFS$TOT_WEIGHT[2]/sum(catchbyarea_LFS$TOT_WEIGHT)*100, digits = 1)`% of the total catch by weight respectively (Table \@ref(tab:bogosloflfs1421catch)). `r .simpleCap(catchbyarea2_LFS$COMMON_NAME[1])` and `r catchbyarea2_LFS$COMMON_NAME[2]`  were the most abundant species by numbers with `r round(catchbyarea2_LFS$TOT_NUMBER[1]/sum(catchbyarea2_LFS$TOT_NUMBER)*100, digits = 1)`% and `r round(catchbyarea2_LFS$TOT_NUMBER[2]/sum(catchbyarea2_LFS$TOT_NUMBER)*100, digits = 1)`% of the total catch by numbers, respectively (Table \@ref(tab:bogosloflfs1421catch)). `r pne_statement`

*Pollock Maturity*

```{r echo = FALSE, message=FALSE, warning=FALSE}
# maturity data

# historical GSI- location for each survey .csv file

# Umnak
# the function that makes plots for the figs/tables should return all the needed values here- using region_id here....
umnak_maturity_data <- plot_abundance_weighted_maturity(ship = ship, 
                                                  survey = survey,  
                                                  region_id = "Umnak")

# get the counts at each stage
umnak_maturity_summary_stage <- umnak_maturity_data[[2]]

# replace "Prespawning" with "pre-spawning" to match text in report
levels(umnak_maturity_summary_stage$MATURITY)[levels(umnak_maturity_summary_stage$MATURITY) == "Prespawning"] <- "pre-spawning"

# identify most common stages
umnak_maturities_male <- umnak_maturity_summary_stage[umnak_maturity_summary_stage$SEX == "Male", ]
umnak_maturities_female <- umnak_maturity_summary_stage[umnak_maturity_summary_stage$SEX == "Female", ]

umnak_most_common_male <- umnak_maturities_male$MATURITY[which.max(umnak_maturities_male$wt_percent)]
umnak_most_common_female <- umnak_maturities_female$MATURITY[which.max(umnak_maturities_female$wt_percent)]

# get the sample sizes
umnak_maturity_nums <- umnak_maturity_data[[5]]

# get the L50
umnak_L50_val <- umnak_maturity_data[[1]]$L50

# and the GSI stats
umnak_GSI_stats <- umnak_maturity_data[[3]]

# and the minimum fork length used in L50 calcs
umnak_min_L50_length <- min(prop_mature$FORK_LENGTH[prop_mature$region == "Umnak"])


# the function that makes plots for the figs/tables should return all the needed values here- using region_id here....
samalga_maturity_data <- plot_abundance_weighted_maturity(ship = ship, 
                                                  survey = survey,  
                                                  region_id = "Samalga")

# Samalga
# get the counts at each stage
samalga_maturity_summary_stage <- samalga_maturity_data[[2]]

# replace "Prespawning" with "pre-spawning" to match text in report
levels(samalga_maturity_summary_stage$MATURITY)[levels(samalga_maturity_summary_stage$MATURITY) == "Prespawning"] <- "pre-spawning"

# identify most common stages
samalga_maturities_male <- samalga_maturity_summary_stage[samalga_maturity_summary_stage$SEX == "Male", ]
samalga_maturities_female <- samalga_maturity_summary_stage[samalga_maturity_summary_stage$SEX == "Female", ]

samalga_most_common_male <- samalga_maturities_male$MATURITY[which.max(samalga_maturities_male$wt_percent)]
samalga_most_common_female <- samalga_maturities_female$MATURITY[which.max(samalga_maturities_female$wt_percent)]

# get the sample sizes
samalga_maturity_nums <- samalga_maturity_data[[5]]

# get the L50
samalga_L50_val <- samalga_maturity_data[[1]]$L50

# and the GSI stats
samalga_GSI_stats <- samalga_maturity_data[[3]]

# and the minimum fork length used in L50 calcs
samalga_min_L50_length <- min(prop_mature$FORK_LENGTH[prop_mature$region == "Samalga"])


# All the data
# Amended the plot_abundance_weighted_maturity function to handle no region.
overall_maturity_data = plot_abundance_weighted_maturity(ship = ship, 
                                                  survey = survey,
                                                  region_id = "")
overall_GSI_stats <- overall_maturity_data[[3]]
```
 
The weighted maturity compositions were different between the Umnak and the Samalga regions. Most female pollock in the Umnak region were in the `r tolower(umnak_most_common_female)` stage of maturity. The maturity composition of females in the Umnak region > 30 cm FL (n = `r umnak_maturity_nums$n[umnak_maturity_nums$SEX == 'Female']`) was `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Female' & umnak_maturity_summary_stage$MATURITY == 'Immature'], digits = 0)`% immature, `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Female' & umnak_maturity_summary_stage$MATURITY == 'Developing'], digits = 0)`% developing, `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Female' & umnak_maturity_summary_stage$MATURITY == 'pre-spawning'], digits = 0)`% pre-spawning, `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Female' & umnak_maturity_summary_stage$MATURITY == 'Spawning'], digits = 0)`% spawning, and `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Female' & umnak_maturity_summary_stage$MATURITY == 'Spent'], digits = 0)`% spent, while the maturity composition of males > 30 cm FL (n = `r umnak_maturity_nums$n[umnak_maturity_nums$SEX == 'Male']`) was `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Male' & umnak_maturity_summary_stage$MATURITY == 'Immature'], digits = 0)`% immature, `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Male' & umnak_maturity_summary_stage$MATURITY == 'Developing'], digits = 0)`% developing, `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Male' & umnak_maturity_summary_stage$MATURITY == 'pre-spawning'], digits = 0)`% pre-spawning, `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Male' & umnak_maturity_summary_stage$MATURITY == 'Spawning'], digits = 0)`% spawning, and `r round(umnak_maturity_summary_stage$wt_percent[umnak_maturity_summary_stage$SEX == 'Male' & umnak_maturity_summary_stage$MATURITY == 'Spent'], digits = 0)`% spent (Fig. \@ref(fig:umnakmaturity)a). The maturity composition of females in the Samalga region > 30 cm FL (n = `r samalga_maturity_nums$n[samalga_maturity_nums$SEX == 'Female']`) was `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Female' & samalga_maturity_summary_stage$MATURITY == 'Immature'], digits = 0)`% immature, `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Female' & samalga_maturity_summary_stage$MATURITY == 'Developing'], digits = 0)`% developing, `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Female' & samalga_maturity_summary_stage$MATURITY == 'pre-spawning'], digits = 0)`% pre-spawning, `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Female' & samalga_maturity_summary_stage$MATURITY == 'Spawning'], digits = 0)`% spawning, and `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Female' & samalga_maturity_summary_stage$MATURITY == 'Spent'], digits = 0)`% spent, while the maturity composition of males > 30 cm FL (n = `r samalga_maturity_nums$n[samalga_maturity_nums$SEX == 'Male']`) was `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Male' & samalga_maturity_summary_stage$MATURITY == 'Immature'], digits = 0)`% immature, `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Male' & samalga_maturity_summary_stage$MATURITY == 'Developing'], digits = 0)`% developing, `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Male' & samalga_maturity_summary_stage$MATURITY == 'pre-spawning'], digits = 0)`% pre-spawning, `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Male' & samalga_maturity_summary_stage$MATURITY == 'Spawning'], digits = 0)`% spawning, and `r round(samalga_maturity_summary_stage$wt_percent[samalga_maturity_summary_stage$SEX == 'Male' & samalga_maturity_summary_stage$MATURITY == 'Spent'], digits = 0)`% spent (Fig. \@ref(fig:samalgamaturity)a). The length at which 50% of female pollock were determined to be reproductively mature (i.e., pre-spawning, spawning, or spent) could not be accurately estimated for either area (Umnak or Samalga) because the female pollock specimens were all mature, and therefore, had a lack of contrast in length and maturity data.  The overall average GSI for pre-spawning mature female pollock observed in 2024 was `r overall_GSI_stats$n_gsi_females`. The average GSI in the Umnak region from  `r umnak_GSI_stats$n_gsi_females` pre-spawning females was `r round(umnak_GSI_stats$mean_weighted_GSI, digits =2) `  $\pm$ `r round(umnak_GSI_stats$std_weighted_GSI, digits =3) ` (Fig. \@ref(fig:umnakmaturity)c, mean $\pm$ standard deviation), which was within 1 standard deviation of the `r last_year` estimate (0.15 $\pm$ 0.03) and the historical mean (`r round(umnak_GSI_stats$wtd_mean_without_current_survey, digits=2) ` $\pm$ `r round(umnak_GSI_stats$wtd_std_without_current_survey, digits =2) `). The average GSI in the Samalga region from  `r samalga_GSI_stats$n_gsi_females` pre-spawning females was `r round(samalga_GSI_stats$mean_weighted_GSI, digits =2) `  $\pm$ `r round(samalga_GSI_stats$std_weighted_GSI, digits =3) ` (Fig. \@ref(fig:samalgamaturity)c, mean $\pm$ standard deviation), which was within 1 standard deviation of the `r last_year` estimate (0.18 $\pm$ 0.004) and the historical mean (`r round(samalga_GSI_stats$wtd_mean_without_current_survey, digits=2) ` $\pm$ `r round(samalga_GSI_stats$wtd_std_without_current_survey, digits =2) `). 

*Distribution and Abundance*

```{r echo = FALSE, message=FALSE, warning=FALSE}
# get the numbers at length by report number
num_bio_at_length_summary <- current_year_pollock_biomass_nums %>%
  # for this report- make sure we're only reporting the requested region
  group_by(LENGTH) %>%
  summarize(
    num_individuals = sum(NUMBERS),
    biomass_kg = sum(BIOMASS)
  ) %>%
  # also report proportions at each length
  mutate(
    numprop = num_individuals / sum(num_individuals),
    bioprop = biomass_kg / sum(biomass_kg)
  )

# summarize by adult (> 30 cm FL) and juvenile (<= 30 cm FL) sized pollock
adultfish <- num_bio_at_length_summary %>%
  filter(LENGTH > 30)
adultfishnumpct <- (sum(adultfish$numprop)) * 100
adultfishbiopct <- (sum(adultfish$bioprop)) * 100

juvfish <- num_bio_at_length_summary %>%
  filter(LENGTH <= 30)
juvfishnumpct <- (sum(juvfish$numprop)) * 100
juvfishbiopct <- (sum(juvfish$bioprop)) * 100

# talk about AGES here- not lengths- if we have ages.
if (isTRUE(age_data)) {
  num_bio_at_age_summary <- shelikof_current_survey_biomass_nums_age %>%
    # for this report- make sure we're only reporting the requested region
    filter(region == region_id) %>%
    group_by(REPORT_NUMBER, region, AGE) %>%
    summarize(
      num_individuals = sum(NUMBERS),
      biomass_kg = sum(BIOMASS)
    ) %>%
    # also report proportions at each length
    mutate(
      numprop = num_individuals / sum(num_individuals),
      bioprop = biomass_kg / sum(biomass_kg)
    )


  age1fish <- num_bio_at_age_summary %>%
    filter(AGE == 1)

  age1numpct <- (sum(age1fish$numprop)) * 100
  age1biopct <- (sum(age1fish$bioprop)) * 100

  # is this right?????- Taina thinks no....
  age2fish <- num_bio_at_age_summary %>%
    filter(AGE == 2)

  age2numpct <- (sum(age2fish$numprop)) * 100
  age2biopct <- (sum(age2fish$bioprop)) * 100
  
  age3fish <- num_bio_at_age_summary %>%
    filter(AGE == 3)

  age3numpct <- (sum(age3fish$numprop)) * 100
  age3biopct <- (sum(age3fish$bioprop)) * 100

  age3plusfish <- num_bio_at_age_summary %>%
    filter(AGE >= 3)

  age3plusnumpct <- (sum(age3plusfish$numprop)) * 100
  age3plusbiopct <- (sum(age3plusfish$bioprop)) * 100

  age4plusfish <- num_bio_at_age_summary %>%
    filter(AGE >= 4)

  age4plusnumpct <- (sum(age4plusfish$numprop)) * 100
  age4plusbiopct <- (sum(age4plusfish$bioprop)) * 100

  # select estimates for specific year classes of interest
  yr2018fish <- num_bio_at_age_summary %>%
    filter(AGE == current_year - 2018)

  yr2018fishnumpct <- (sum(yr2018fish$numprop)) * 100
  yr2018fishbiopct <- (sum(yr2018fish$bioprop)) * 100

  yr2017fish <- num_bio_at_age_summary %>%
    filter(AGE == current_year - 2017)

  yr2017fishnumpct <- (sum(yr2017fish$numprop)) * 100
  yr2017fishbiopct <- (sum(yr2017fish$bioprop)) * 100

  yr2012fish <- num_bio_at_age_summary %>%
    filter(AGE == current_year - 2012)

  yr2012fishnumpct <- (sum(yr2012fish$numprop)) * 100
  yr2012fishbiopct <- (sum(yr2012fish$bioprop)) * 100
}

# and overall
rawbio <- sum(num_bio_at_length_summary$biomass_kg)
rawnum <- sum(num_bio_at_length_summary$num_individuals)

# compare to last year's biomass/nums
last_year_vals <- historical_surveys_pollock_totals_by_length %>%
  # for this report- make sure we're only reporting the requested region
  filter(region == region_id & year == last_year) %>%
  group_by(year) %>%
  summarize(
    num_individuals = sum(NUMBERS),
    biomass_kg = sum(BIOMASS)
  )

# and get the current survey as a percent of last year biomass
# pctoflastyr=((last_year_vals$biomass_kg-rawbio)/last_year_vals$biomass_kg)*100
biomass_change_from_last_year <- (rawbio - last_year_vals$biomass_kg) / last_year_vals$biomass_kg * 100

# Here we amend the code to just generate the mean biomass without pre and post sel and without regions
# Everything that is in the data frame is for each survey
meanHistBiomass <- calculate_mean_historical_biomass_function(historical_surveys_pollock_totals_by_length)

# calculate the percent of the historic biomass
pctofhistoric <- (rawbio / 1e6) / meanHistBiomass * 100

# or, as a % change from historic (in this case 48% decline from historic)
# pctofhistoric = ((rawbio/1e6)- meanHistBiomass)/meanHistBiomass * 100

# if you don't have ages just add an NA for now
if (!isTRUE(age_data)) {
  age1numpct <- NA
  age1biopct <- NA
  age2numpct <- NA
  age2biopct <- NA
  age3fishnumpct <- NA
  age3fishbiopct <- NA
  age3plusnumpct <- NA
  age3plusbiopct <- NA
  age4plusnumpct <- NA
  age4plusbiopct <- NA
  yr2012fishbiopct <- NA
  yr2017fishbiopct <- NA
  yr2018fishbiopct <- NA
}
```

```{r echo = FALSE, message=FALSE, warning=FALSE}

# We aren't currently doing bottom referenced data for Bogoslof, so changed this a bit
# to handle just working with surface referenced data sets
if (!is.null(vertical_dist_surf_ref_biomass_nums_by_length)) {

  # for the surface-referenced data, calculate the total biomass/nums within each layer
  surface_referenced_summary <- vertical_dist_surf_ref_biomass_nums_by_length %>%
    # limit things to the shelikof survey
    filter(SPECIES_CODE == 21740) %>%
    # report depth as the range from upper reference to be consistent;
    # label observations by size class and year
    mutate(size_class = ifelse(LENGTH <= pollock_size_cutoff, "juvenile_layer_biomass", "adult_layer_biomass"))


  mwd_surf_ref <- surface_referenced_summary %>%
    group_by(year, depth, size_class) %>%
    summarize(
      layer_biomass = sum(BIOMASS),
      layer_nums = sum(NUMBERS)
    ) %>%
    group_by(year, size_class) %>%
    summarize(mwd = sum((layer_biomass / sum(layer_biomass)) * depth)) %>%
    mutate(ref = "surface")


  # what were the predominant pollock depths for adults?
  # we'll take this as the middle 50% of the distribution from the surface, i.e. the inter-quartile range
  most_common_depth <- surface_referenced_summary %>%
    group_by(year, depth, size_class) %>%
    # sum biomass/numbers in each layer/size class
    summarize(
      layer_biomass = sum(BIOMASS),
      layer_nums = sum(NUMBERS)
    ) %>%
    # to be safe, arrange by depth
    arrange(depth)


  # and calculate the adult 75% depth quantile (0.125- 0.875 of biomass) weighted by biomass
  adult_common_depths <- most_common_depth[most_common_depth$size_class == "adult_layer_biomass" &
    most_common_depth$year == current_year, ]

  adult_common_depths <- Hmisc::wtd.quantile(adult_common_depths$depth,
    weights = adult_common_depths$layer_biomass,
    probs = c(0.125, 0.875)
  )


  # and calculate the juveline 75% depth quantile (0.125- 0.875 of biomass) weighted by biomass
  juvenile_common_depths <- most_common_depth[most_common_depth$size_class == "juvenile_layer_biomass" &
    most_common_depth$year == current_year, ]

  juvenile_common_depths <- Hmisc::wtd.quantile(juvenile_common_depths$depth,
    weights = juvenile_common_depths$layer_biomass,
    probs = c(0.125, 0.875)
  )


  # compare to last 4 years- how did the mean weighted pollock depth from surface compare?
  region_only_surveys <- unique(vertical_dist_surf_ref_biomass_nums_by_length$year[vertical_dist_surf_ref_biomass_nums_by_length$region == region_id])
  
  last_4_years <- region_only_surveys[(length(region_only_surveys) - 4):(length(region_only_surveys) - 1)]

  # compare to last year
  compare_mwd <- function(comparison_year) {
    # compare the current survey to a previous survey- for surface-referenced adults
    comp_value <- mwd_surf_ref$mwd[mwd_surf_ref$year == current_year & mwd_surf_ref$size_class == "adult_layer_biomass"] -
      mwd_surf_ref$mwd[mwd_surf_ref$year == comparison_year & mwd_surf_ref$size_class == "adult_layer_biomass"]

    # return a dataframe with the comparison year, and the comparison
    return(data.frame(comparison_year, comp_value))
  }

  # get the previous suvey comparisons
  last_4_comps <- map_dfr(last_4_years, compare_mwd)

  # note that positive values imply deeper than previous comparison, negative shallower! We use this to build a comparison sentence
  last_4_comps$current_survey_comp <- ifelse(last_4_comps$comp_value > 0, "deeper", "shallower")

  # build a statement describing how things compare to the last 4 years
  previous_4_years_statement <- ifelse(all(last_4_comps$current_survey_comp == "deeper"),
    "deeper",
    ifelse(all(last_4_comps$current_survey_comp == "shallower"),
      "shallower",
      paste0(
        "deeper than ", length(last_4_comps$current_survey_comp[last_4_comps$current_survey_comp == "deeper"]),
        " out of 4 of the last survey"
      )
    )
  )
}

```


Adult pollock (defined as > 30 cm FL) were detected throughout the survey area near Bogoslof Island, with the largest aggregations concentrated north of the eastern point of Umnak Island and north of Samalga Pass (Fig. \@ref(fig:bogoslofsticks)). Compared to previous years, this distribution was consistent with two large aggregations in these areas. 

Most adult pollock (comprising `r round(adultfishbiopct,1)`% of total biomass) were detected between depths of `r adult_common_depths[[1]]`–`r adult_common_depths[[2]]` m (Fig. \@ref(fig:violins)a). No juvenile pollock (<= 30 cm FL) were detected, although they were observed in 2014 and 2020 (Fig. \@ref(fig:violins)b). Adult pollock depth distributions in `r current_year` were `r  last_4_comps$current_survey_comp[last_4_comps$comparison_year == last_year]` than those in `r last_year` and `r previous_4_years_statement` than in the prior 4 years (Fig. \@ref(fig:violins)a, b).

A total of `r print_n_decimal(rawnum/1e6 , 1) ` million pollock weighing `r print_n_decimal(rawbio/1000, 1)` t were estimated to be in region near Bogoslof Island at the time of the survey (Tables \@ref(tab:biotable), \@ref(tab:numlength)). The `r current_year` biomass `r ifelse(biomass_change_from_last_year > 0, 'increased', 'decreased')` `r print_n_decimal(abs(biomass_change_from_last_year), 1)`% from that observed in `r last_year` (`r print_n_decimal(last_year_vals$biomass_kg/1000, 0)` t) and was `r round(pctofhistoric, digits = 1)`% of the historical mean of `r print_n_decimal(meanHistBiomass, 1)` thousand tons (Table \@ref(tab:biotable), Fig. \@ref(fig:biocomps)). The relative estimation error of the `r current_year` biomass estimate based on the 1-D geostatistical analysis was `r eva_perc`% (Table \@ref(tab:biotable)).


*Effects of Net Selectivity Corrections*

```{r, shelikof_selectivity_paragraph, echo = FALSE, message=FALSE, warning=FALSE}
# Current year non-selectivity based estimate- numbers of age 1 fish for McKelvey index and comparisons; we can get this from our comparisons dataset- it has pollock summarized by length
NoSelect <- analysis_comparisons %>%
  # get the non-selectivity dataset for the region; this relies on having that as a comparison dataset and assumes the first comparison
  # is non-selectivity
  filter(DATA_SET_ID == comp_data_sets[1] & ANALYSIS_ID == comp_analyses[1])

pctofprimarybio <- ((sum(NoSelect$BIOMASS) - rawbio) / rawbio) * 100
pctofprimarynum <- ((sum(NoSelect$NUMBERS) - rawnum) / rawnum) * 100

age1fishnoselect <- NoSelect %>%
  filter(LENGTH <= 16)
```

The results presented here account for escapement of organisms from the net based on the prior LFS1421 selectivity values obtained from catches in the codend and recapture nets from the 2020 winter Bogoslof survey. These results also reflect adjustments to the backscatter allotted to the target species by removing backscatter that would be attributable to other species based on the catch composition of the nearest haul and their estimated scattering properties. While this reflects analysis procedures in the winter Bogoslof survey time series since 2020, analyses in previous years have not fully taken these factors into account. Thus an alternate analysis was conducted that would more closely approximate analyses in prior years for comparison, and resulting abundances are presented (Fig. \@ref(fig:analysiscomps)). Specifically, an alternate analysis was conducted that did not include the effect of net selectivity (referred to as the 'no-selectivity' analysis below). This is similar to the comparison performed in 2020 to evaluate the effects of net selectivity corrections [**McKelvey and Levine, 2023**]. 

The no-selectivity analysis for `r current_year` generated an overall `r ifelse(pctofprimarynum <0, 'decrease', 'increase')` of `r print_n_decimal(abs(pctofprimarynum), 2)`% by numbers (to `r print_n_decimal(sum(NoSelect$NUMBERS)/1e6, 0)` million) and an `r ifelse(pctofprimarybio <0, 'decrease', 'increase')` of `r print_n_decimal(abs(pctofprimarybio), 2)`% by weight (to `r print_n_decimal(sum(NoSelect$BIOMASS, na.rm = TRUE)/1000,0)` t) for pollock in the area compared to the primary analysis (i.e. "selectivity corrected", Fig. \@ref(fig:analysiscomps)). The negligible effect of net selectivity corrections on the `r current_year` primary analysis estimates is expected given the lack of juvenile pollock (≤ 30 cm FL) observations in the survey region (Fig. \@ref(fig:bogoslofbionumslength)).


*Survey Time Series*
