#### MACE `r combine_words(unique(current_year_pollock_biomass_nums$region))` `r current_year` Gulf of Alaska acoustic trawl survey: pollock results

**Survey:** `r format(survey_shelikof)`

```{r totals_by_region, echo = FALSE, message=FALSE, warning=FALSE}
# sum up totals in each region
totals_by_region <- stock_assess_bio_nums_length_region %>%
  group_by(region) %>%
  summarize(
    biomass_ton = sum(biomass_ton),
    number_million_fish = sum(number_million_fish)
  ) %>%
  mutate(
    biomass_statement = paste0(region, "; ", print_n_decimal(biomass_ton, n_decimals = 3), " t"),
    numbers_statement = paste0(region, "; ", print_n_decimal(number_million_fish, n_decimals = 3), " million fish")
  )
```

Total pollock biomass: `r combine_words(totals_by_region$biomass_statement)`. 

Total pollock numbers:  `r combine_words(totals_by_region$numbers_statement)`.

```{r prop_by_age, echo = FALSE, message=FALSE, warning=FALSE}
if (age_data == TRUE) {
  prop_by_age_table <- pk_by_age %>%
    ungroup() %>%
    select(-SURVEY) %>%
    # round to 8 decimals for display
    mutate(prop_num = round(prop_num, digits = 8)) %>%
    select(age, prop_num) %>%
    data.table::transpose(make.names = TRUE)

  # display a table
  flextable::flextable(prop_by_age_table) %>%
    flextable::fontsize(size = 8, part = "all") %>%
    flextable::set_caption(caption = "Numbers at age (proportions)") %>%
    flextable::fit_to_width(max_width = 7)
}
```

**Is this an update to a currently provided dataset?** `r ifelse(lengths_data_check == TRUE, 'yes', 'no')`

**If this is an update, what are the notable changes?**


```{r compare_biomass, echo = FALSE, message=FALSE, warning=FALSE}
# does the total biomass differ?
if (lengths_data_check == TRUE) {
  # compute the updated total biomass
  new_biomass_length_t <- sum(stock_assess_bio_nums_length_region$biomass_ton)

  # is this equal to the old? (round to 4th decimal to be safe)
  same_biomass_length <- round(old_biomass_length_t, digits = 4) == round(new_biomass_length_t, digits = 4)

  # if not- what is the difference?
  if (!same_biomass_length == TRUE) {
    biomass_length_diff_t <- new_biomass_length_t - old_biomass_length_t

    biomass_comp_length_sentence <- paste0("The updated total biomass is ", print_n_decimal(new_biomass_length_t, n_decimals = 4), " t, a difference of ", print_n_decimal(biomass_length_diff_t, n_decimals = 4), " t from the initially provided biomass of ", print_n_decimal(old_biomass_length_t, n_decimals = 4), " t. ")
  }

  # if the biomass is the same- report this
  if (same_biomass_length == TRUE) {
    biomass_comp_length_sentence <- ""
  }
}

if (lengths_data_check != TRUE) {
  biomass_comp_length_sentence <- ""
}
```

`r biomass_comp_length_sentence`

```{r ages_checks, echo = FALSE, message=FALSE, warning=FALSE}
# are we sending ages for the first time? In this case, the old result won't have ages, but we will have age data now
if (ages_data_check == FALSE & age_data == TRUE) {
  age_update_sentence <- "Age composition data have been added."
}

# are there any differences in the age data? Check in case we have already got age data
if (ages_data_check == TRUE & age_data == TRUE) {
  # total biomass equal?
  new_biomass_age_t <- sum(shelikof_stock_assess_bio_nums_age_region$biomass_ton)

  # is this equal to the old? (round to 4th decimal to be safe)
  same_biomass_age <- round(old_biomass_age_t, digits = 4) == round(new_biomass_age_t, digits = 4)

  # if not- what is the difference?
  if (!same_biomass_length == TRUE) {
    biomass_age_diff_t <- new_biomass_age_t - old_biomass_age_t

    biomass_comp_age_sentence <- paste0("The updated total biomass is ", print_n_decimal(new_biomass_age_t, n_decimals = 4), " t, a decline of ", print_n_decimal(biomass_age_diff_t, n_decimals = 4), " t from the initially provided biomass of ", print_n_decimal(old_biomass_age_t, n_decimals = 4), " t.")
  }

  # if they are the same, no need for a note
  if (same_biomass_length == TRUE) {
    biomass_comp_age_sentence <- ""
  }
}
```

`r if (ages_data_check == FALSE & age_data == TRUE){age_update_sentence}`

`r if (ages_data_check == TRUE & age_data == TRUE){biomass_comp_age_sentence}`


**Included output files:**

```{r id_files, echo = FALSE, message=FALSE, warning=FALSE}
# BY LENGTH

# Biomass and abundance by 1 cm length bins for each surveyed area
all_files_list <- list.files("stock_assessment_output/", pattern = "*.csv")
bio_abund_length <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "biomass_num_length_by_region"))]

# Total biomass by management area
biomass_mgmt_area <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "biomass_num_length_by_INPFC"))]

# Relative Estimation Error
rel_est_err <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "relative_estimation_error"))]

# Number of bottom trawls and number of midwater trawls
n_trawls <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "n_trawls"))]

# Number of measured pollock (length) by sex
n_lengths <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "lengths_by_sex"))]

# Abundance-weighted maturity at length data: not for summer goa

# specimen data including ages and maturity determinations.
specimens <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "specimen_data"))]

# BY AGE

# Biomass and abundance by age
bio_abund_age <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "biomass_num_age"))]

# Number of aged pollock by sex
n_ages <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "ages_by_sex"))]

# Abundance-weighted maturity at length data:
weighted_maturity_length <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "weighted_L50_mature"))]


# Abundance-weighted maturity at length data:
weighted_maturity_age <- all_files_list[which(stringr::str_detect(string = all_files_list, pattern = "weighted_A50_mature"))]
```

Biomass and abundance by 1 cm length bins for each surveyed area: *`r bio_abund_length`*

Biomass and abundance by age: *`r ifelse(age_data == TRUE, bio_abund_length, 'Age data is not yet available.')`*

Total biomass by management area: *`r biomass_mgmt_area`*

Number of measured pollock (length) by sex: *`r n_lengths`*

Number of aged pollock by sex: *`r ifelse(age_data == TRUE, n_ages, 'Age data is not yet available.')`*

Relative Estimation Error:  *`r rel_est_err`*

Number of midwater and bottom trawls: *`r n_trawls`*

Specimen data: *`r specimens`*

Maturity at length (weighted by local abundance): *`r weighted_maturity_length``*

Maturity at age (weighted by local abundance): *`r ifelse(age_data == TRUE, weighted_maturity_age, 'Age data is not yet available.')`*

\pagebreak

**Survey extent**

```{r survey_extent_map, echo = FALSE, message=FALSE, warning=FALSE, fig.width= 6, fig.height= 6, dpi=300}
comp_map <- make_survey_location_comparison_map(all_survey_intervals = historical_interval_data, current_survey_intervals = current_year_interval_data)

comp_map

```

\pagebreak

**Survey timing**
```{r survey_timing_update, echo = FALSE, message=FALSE, warning=FALSE, fig.width= 6, fig.height= 6, dpi=300}

# open up the historical survey timing dataset
load('historical_data/shelikof_survey_timing.rda')

# get the current survey summarized to match historical format
current_timing_data <- current_year_interval_data %>%
  st_drop_geometry() %>%
  # we only report shelikof strait here, so limit to this
  filter(region == "Shelikof Strait") %>%
  group_by(year) %>%
  summarize(
    start = min(lubridate::date(START_TIME)),
    end = max(lubridate::date(START_TIME))
  )

# format the current timing data for joining with the historic
#for plotting- set all year components to 1900
lubridate::year(current_timing_data$start) <- 1900
lubridate::year(current_timing_data$end) <- 1900


# pull in the female prespawning, spent values and present as percents
maturity_data <- plot_abundance_weighted_maturity(ship = ship_shelikof, 
                                                  survey = survey_shelikof,  
                                                  region_id = "Shelikof Strait")

#get the summary we need
current_maturity_data <- maturity_data[[2]]

maturity_to_join <- current_maturity_data %>%
  filter(SEX == 'Female') %>%
  # we only care about prespawn/spawning/spent in this case
  filter(MATURITY %in% c("Prespawning", "Spawning", "Spent"))%>%
  mutate(
    mat_stage = ifelse(MATURITY %in% c("Spawning", "Spent"),
         'spawning_spent', 
         "prespawn")
   ) %>%
  group_by(mat_stage) %>%
  summarize(wt_percent = sum(wt_percent)) %>%
  pivot_wider(names_from = mat_stage, values_from = wt_percent)

# add a row to the summary dataframe
new_row <- data.frame(current_timing_data$year, current_timing_data$start, current_timing_data$end, maturity_to_join$prespawn, maturity_to_join$spawning_spent)

colnames(new_row) <- colnames(shelikof_timing)

# check- if there is a datapoint for the current survey, replace with the current values 
if (current_year %in% shelikof_timing$year){
  
  # get rid of this year- we'll update to be safe; this will be needed in cases where
  # a more recent analysis has changed values
  shelikof_timing <- shelikof_timing %>%
    filter(year != current_year)
  
}

# append the most up-top-date info to to the historical data
shelikof_timing <- bind_rows(shelikof_timing, new_row)

#and save the dataset
save(shelikof_timing, file = 'historical_data/shelikof_survey_timing.rda')

```

```{r survey_timing_gantt, echo = FALSE, message=FALSE, warning=FALSE, fig.width= 6, fig.height= 7, dpi=300}

shelikof_gantt <- shelikof_timing %>%
  select(!c('prespawn', 'spawning_spent')) %>%
  pivot_longer(cols = -c('year'), names_to = 'state', values_to = 'time') %>%
  # define a plotting color- red for current survey, otherwise black
  mutate(current_year = ifelse(year == unique(current_year_interval_data$year),
                TRUE,
                FALSE) 
         )

# plot everything
ggplot(shelikof_gantt, aes(x = time, y = year, group=year, color = current_year)) +
  geom_line(size = 1.25) +
  scale_y_reverse() +
  scale_color_manual(values = c('black', 'red')) +
  labs(x="Date", y="Survey Year", title="Shelikof Winter AT Survey Dates") +
  theme_bw() +
  cruise_report_plots_theme +
  theme(legend.position = 'none')


```


```{r survey_timing_maturity, echo = FALSE, message=FALSE, warning=FALSE, fig.width= 6, fig.height= 4, dpi=300}

#plot the maturity too
shelikof_maturity <- shelikof_timing %>%
  select('year', 'prespawn', 'spawning_spent') %>%
  pivot_longer(cols = -c("year"), names_to = 'stage', values_to = 'perc')

ggplot(shelikof_maturity, aes(x = year, y = perc, color = stage))+
  geom_line(size = 1.5, alpha = 0.6)+
  scale_color_manual(values = c('black', 'red')) +
  labs(x="Survey Year", y="Percent", title="Shelikof winter female spawning states") +
  theme_bw() +
   cruise_report_plots_theme 


```